---
title: "Analysis of HSB2 Data"
output:
  html_document:
    df_print: paged
---
The hsb2 data are demographics and test scores for a random sample of high school seniors in the nation. This will be an analysis of those scores.

To pull data from Data folder, need to use here function
```{r include=FALSE}
library(here)
```

### The relationship of SES to math performance

```{r include=FALSE}
hsb2 <- read.csv(here("Data", "hsb2.csv"))
```

Here are side-by-side boxplots of math scores by SES levels.

```{r echo=FALSE}
hsb2$ses <- factor(hsb2$ses, 
                   levels = c(1:3),
                   labels = c("low", "middle", "high"),
                   ordered = TRUE)

boxplot(hsb2$math ~ hsb2$ses,
        xlab = "SES Category",
        ylab = "Math Test Score",
        main = "Math Test Scores by SES Category")
```

Here are the five-number summaries, means, and standard deviations.

```{r echo=FALSE}
tapply(hsb2$math, hsb2$ses, fivenum)
tapply(hsb2$math, hsb2$ses, mean)
tapply(hsb2$math, hsb2$ses, sd)
```


